---
title: "Linear Model with Prediction"
author: "Fernando D Velasquez"
date: "4/19/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tigerstats)
library(tidyverse)
```

Read about the data from the website where it is staged.  Then form three regression models; Model1 is SIMS~ARM, Model2 is SIMS~GRIP, and Model3 is SIMS~ARM+GRIP. For each model find a 95% prediction interval of SIMS given a value of 94  for GRIP and 88 for ARM. Compare Model1 with Model3 using anova. Write it up in a markdown document, push the project up to your github account and submit it back to canvas as link. 



```{r}
data <- read.csv(file="https://onlinestatbook.com/case_studies_rvls/physical_strength/data.txt",sep="",header=TRUE)  
```

###Plot scatterplot

```{r}
plot(SIMS~ARM,data=data)
```

##Now with ggplot - first select the basic data

```{r}
basicNN <- ggplot(data,aes(y=SIMS,x=ARM))
```
##Now add in scatterplot

```{r}
basicNN + geom_point()+ geom_smooth(method=lm)
```
  

```{r}
model1= lm(SIMS~ARM,data=data)
summary(model1)
```
The adjusted R-Squared for this model is 0.467.  

###Plot scatterplot

```{r}
plot(SIMS~GRIP,data=data)
```

##Now with ggplot - first select the basic data

```{r}
basicNN <- ggplot(data,aes(y=SIMS,x=GRIP))
```
##Now add in scatterplot

```{r}
basicNN + geom_point()+ geom_smooth(method=lm)
```
  


```{r}
model2= lm(SIMS~GRIP,data=data)
summary(model2)
```
The adjusted R-Squared for model number #2 is 0.4053 which is smaller than model number #1.    

