---
title: "Linear Model with Prediction"
author: "Fernando D Velasquez"
date: "4/19/2021"
output:
    html_document:
        toc: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tigerstats)
library(tidyverse)
```

Read about the data from the website where it is staged.  Then form three regression models; Model1 is SIMS~ARM, Model2 is SIMS~GRIP, and Model3 is SIMS~ARM+GRIP. For each model find a 95% prediction interval of SIMS given a value of 94  for GRIP and 88 for ARM. Compare Model1 with Model3 using anova. Write it up in a markdown document, push the project up to your github account and submit it back to canvas as link. 



```{r}
data <- read.csv(file="https://onlinestatbook.com/case_studies_rvls/physical_strength/data.txt",sep="",header=TRUE)  
```

# Model 1  

### Plot scatterplot

```{r}
plot(SIMS~ARM,data=data)
```

### Now with ggplot - first select the basic data

```{r}
basicNN <- ggplot(data,aes(y=SIMS,x=ARM))
```
### Now add in scatterplot

```{r}
basicNN + geom_point()+ geom_smooth(method=lm)
```

  
Equation for the line is SIMS= -4.1 + 0.05*ARM. The scatter plot shows a positive relation between ARM and SIMS. 


```{r}
model1= lm(SIMS~ARM,data=data)
summary(model1)
```

The adjusted R-Squared for this model is 0.467 and the Residual standard error is 1.226

### Prediction 1
```{r}
newdata= data.frame(GRIP=94, ARM=88)
predict(model1,newdata,interval="prediction")
```

# Model 2

### Plot scatterplot

```{r}
plot(SIMS~GRIP,data=data)
```

### Now with ggplot - first select the basic data

```{r}
basicNN <- ggplot(data,aes(y=SIMS,x=GRIP))
```
### Now add in scatterplot

```{r}
basicNN + geom_point()+ geom_smooth(method=lm)
```
  
  
Equation of the line is SIMS= -4.9 + 0.04 *GRIP. The scatter plot shows a positive relation between SIMS and GRIP.  

```{r}
model2= lm(SIMS~GRIP,data=data)
summary(model2)
```

### Prediction 2

```{r}
predict(model2,newdata,interval="prediction")
```

The adjusted R-Squared for model number #2 is 0.4053 which is smaller than model number #1. The Residual standard error is 1.295 which is bigger than model 1.  

# Model 3 

### Inferential  (Build linear model)
  
```{r}
model3 <- lm(SIMS~ARM + GRIP,data=data)
summary.lm(model3)
```


### Prediction 3
```{r}
predict(model3,newdata,interval="prediction")
```

# COMPARE THE MODELS 

```{r}
anova(model1,model3)
```
The anova compares model 1 and 3 as well the null hypothesis shows that their is no difference to predict SIMS. The alternative hypothesis says that their is a difference. The difference to predict SIMS is due to no chance as the p value is too small. Both the standard deviation and adjusted R squared indicated that model 3 (ARM+Grip) is the best model as the prediction is 0.15 and the 95% confidence interval is -2.1 to 2.4.
